### 2021-02-16 referee_response.md

We have added a histogram (which was previously published in Lingard et al. 2020) as a new Figure 3 in Section 2.2. There is also a histogram, and an investigation of how pitch angle varies with stellar mass in Section 3.1.

> Since a sample of 98 galaxies were shown twice to (different?) volunteers, it is of interest to compare the results for the same galaxies: did the resulting pitch angles, number of arms, etc. all agree ? One of the data files available on the GitHub website indicates that this is not the case, but that website is poorly documented.

 In this set of 98 galaxies, we find that 93% have the number of arms the same within +/-1 (53% have exactly the same number of arms).

 We have expanded the reasons why we sometimes miss arms (generally in the clustering part of the process) below.

 Because of the Bayesian method used to obtain the final pitch angles, running this twice for the validation set, while potentially interesting, is not something we are able to do at this time. We are confident that the errors we report on the pitch angles capture this potential variation.

** TODO CONFIRM THE ABOVE **

@@

> 3. Section 3.1

> You report a final sample of 139 galaxies with 261 spiral arms, i.e. less than 2 arms per galaxy. Please give details of why this is so. Please also list how many of the galaxies are multiarmed, and state the number of arms.

When we looked into this we found this needed to be updated to 129 galaxies with 247 spiral arms which is closer to two arms per galaxy (1.9). We are unsure of the reason for this discrepancy, it may have been a typo, or left over from an earlier run.

Here is the complete breakdown of number of arms per galaxy:

159 total galaxies, 129 of which with identified spiral arms
247 total spiral arms
238,433 total points
----------------------------------------------------------------------
 30  galaxies had 0 arm(s)
 38  galaxies had 1 arm(s)
 68  galaxies had 2 arm(s)
 19  galaxies had 3 arm(s)
 4   galaxies had 4 arm(s)

This has been entered into the text.

@@

> In Figure 4 I count about 40 1-armed spirals, 22 3-armed spirals, 14 4-armed spirals, and about 63 2-armed spirals (more difficult to count). Why are there so many 1-armed spirals, and why for these, for pitch angles below about 14 degrees, is PHI_arm not equal to PHI_gal ?

 We have found that in some cases, while volunteers drew two arms, the clustering/aggregation code was unable to cluster them, so the final method reported a single arm. This happened in **TODO** cases, and is expected behaviour when clustering noisy data. The presence of this fraction of single armed galaxies drives the average number of arms per galaxy down below the real value, and because the most common number of actual arms is two, it is particularly notable in resulting in reports of one-armed galaxies.

We have added to the previously existing explanation of why PHI_gal is consistently below PHI_gal at low values of pitch angle for a single arm at the end of section 3.1 to make clearer the point that it's related to finding the mean of a broad, but skewed (truncated at zero) distribution.

### 2021-02-16 sections/method.tex
Few more numbers.

Some galaxies in \citet{2020arXiv200610450L} were shown to volunteers a second time in a repeat validation subset to create a second aggregate model used to test internal consistency. We combine the 30 classifications of galaxies in this validation subset with the 30 original classifications. Clustering of drawn spiral arms and cleaning of points was then performed as detailed in \citet{2020arXiv200610450L}. We remove any galaxies for which no spiral arms were identified, resulting in a hierarchical data structure of {\bf 129 galaxies, 247 spiral arms and 238,433 points}.

>>>>

Some galaxies in \citet{2020arXiv200610450L} were shown to volunteers a second time in a repeat validation subset to create a second aggregate model used to test internal consistency. {\bf Section 3.2 of \citet{2020arXiv200610450L} presents a comparison if these classifications to investigate volunteer consistency. We can see that arm number is highly reliable within $\pm1$ (93\% galaxies have arm number counts which agree in this range; 53\% have exactly identical arm number counts).} In this work, we combine the 30 classifications of galaxies in this validation subset with the 30 original classifications. Clustering of drawn spiral arms and cleaning of points was then performed as detailed in \citet{2020arXiv200610450L}. We remove any galaxies for which no spiral arms were identified, resulting in a hierarchical data structure of {\bf 129 galaxies, 247 spiral arms and 238,433 points. This breaks down further to 68 galaxies (53\% of the sample) having two arms identified (meaning marked by the users, and clustered into an arm), 19 (15\%) with three such arms, 4 (3\%) with four, and the remainder (38 or 29\%) with a single identified arm. We believe that our reported number of arms per galaxy is in many cases an underestimate, and since the most common number of arms is two, this most often results in a single arm being measured when two are present. The most common way we miss an arm is if the clustering did not converge when users have appeared to identify a second arm. This happens in XX\% of galaxies, so we don't recommend using these statistics to make general conclusions about the number of arms per galaxy.}
